R for Clinical Study Reports and Submission

### 2024-02-20 slides/china-r.Rmd
Update R submission site URL

- R-based submission pilots to FDA:
  - <https://rconsortium.github.io/r-submission-site/>
  - Focus on improving practices of R-based clinical trial regulatory submission.

>>>>

- R-based submission pilots to FDA:
  - <https://rconsortium.github.io/submissions-wg/>
  - Focus on improving practices of R-based clinical trial regulatory submission.
